R Notebook

### 2021-05-06 FEM_R/results.Rmd
Changed a lot of the visualisations to use geom_smooth() instead of geom_line()

@@

  p <- ggplot(data = melted, aes(x = year, y = Scenario, color = variable)) +
          geom_line() +
          labs(title = paste(int_name, dis, sep = ' - '), x = 'Year', y = 'Prevalence')

@@

  p1 <-ggplot(data = filter(pivot.merged, Feature == 'bmi'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'Average BMI', x = 'Age', y = 'BMI')

@@

  p2 <- ggplot(data = filter(pivot.merged, Feature == 'heart'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'Heart Disease', x = 'Age', y = 'Prevalence')

@@

  p3 <- ggplot(data = filter(pivot.merged, Feature == 'stroke'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'Stroke', x = 'Age', y = 'Prevalence')

@@

  p4 <- ggplot(data = filter(pivot.merged, Feature == 'diabetes'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'Diabetes', x = 'Age', y = 'Prevalence')

@@

  p5 <- ggplot(data = filter(pivot.merged, Feature == 'employed'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'Employed', x = 'Age', y = 'Prevalence')

  p6 <- ggplot(data = filter(pivot.merged, Feature == 'retired'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'Retired', x = 'Age', y = 'Prevalence')

  p7 <- ggplot(data = filter(pivot.merged, Feature == 'adl'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'ADLs', x = 'Age', y = 'Prevalence')

  p8 <- ggplot(data = filter(pivot.merged, Feature == 'iadl'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'IADLs', x = 'Age', y = 'Prevalence')

@@

visCDComparison(c, s, 'No Smoke', 'cancre')
visCDComparison(c, s, 'No Smoke', 'diabe')
visCDComparison(c, s, 'No Smoke', 'hearte')
visCDComparison(c, s, 'No Smoke', 'lunge')
visCDComparison(c, s, 'No Smoke', 'stroke')
visCDComparison(c, s, 'No Smoke', 'smoken')
visCDComparison(c, s, 'No Smoke', 'employed')
visCDComparison(c, s, 'No Smoke', 'retired')
visCDComparison(c, s, 'No Smoke', 'anyadl')
visCDComparison(c, s, 'No Smoke', 'anyiadl')

@@

visList <- visCDComparisonBMI(c, bmi1, bmi2, bmi3, cds)

@@

>>>>

  return(p1)

}

visCDComparisonCohort <- function(cohort, int, int_name, cd, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  selcohort <- cohort %>%
              dplyr::select(c('Age', all_of(var))) %>%
              dplyr::rename('Cohort' = var)

  selInt <- int %>%
              dplyr::select(c('Age', all_of(var))) %>%
              dplyr::rename('Intervention' = var)

  melted <- merge(selcohort, selInt, by = 'year') %>%
              reshape2::melt(id.var = 'Age', value.name = 'Scenario')

  p <- ggplot(data = melted, aes(x = Age, y = Scenario, color = variable)) +
          geom_smooth(lwd = 0.5) +
          labs(title = paste(int_name, dis, sep = ' - '), x = 'Year', y = 'Prevalence')

@@

  p <- ggplot(data = melted, aes(x = year, y = Scenario, color = variable)) +
          geom_smooth(lwd = 0.5) +
          labs(title = paste(int_name, dis, sep = ' - '), x = 'Year', y = 'Prevalence')

@@

  p1 <-ggplot(data = filter(pivot.merged, Feature == 'bmi'), aes(x = Age, y = Value, color = Scenario)) +
        geom_smooth(lwd = 0.5) +
        labs(title = 'Average BMI', x = 'Age', y = 'BMI')

@@

  p2 <- ggplot(data = filter(pivot.merged, Feature == 'heart'), aes(x = Age, y = Value, color = Scenario)) +
        geom_smooth(lwd = 0.5) +
        labs(title = 'Heart Disease', x = 'Age', y = 'Prevalence')

@@

  p3 <- ggplot(data = filter(pivot.merged, Feature == 'stroke'), aes(x = Age, y = Value, color = Scenario)) +
        geom_smooth(lwd = 0.5) +
        labs(title = 'Stroke', x = 'Age', y = 'Prevalence')

@@

  p4 <- ggplot(data = filter(pivot.merged, Feature == 'diabetes'), aes(x = Age, y = Value, color = Scenario)) +
        geom_smooth(lwd = 0.5) +
        labs(title = 'Diabetes', x = 'Age', y = 'Prevalence')

@@

  p5 <- ggplot(data = filter(pivot.merged, Feature == 'employed'), aes(x = Age, y = Value, color = Scenario)) +
        geom_smooth(lwd = 0.5) +
        labs(title = 'Employed', x = 'Age', y = 'Prevalence')

  p6 <- ggplot(data = filter(pivot.merged, Feature == 'retired'), aes(x = Age, y = Value, color = Scenario)) +
        geom_smooth(lwd = 0.5) +
        labs(title = 'Retired', x = 'Age', y = 'Prevalence')

  p7 <- ggplot(data = filter(pivot.merged, Feature == 'adl'), aes(x = Age, y = Value, color = Scenario)) +
        geom_smooth(lwd = 0.5) +
        labs(title = 'ADLs', x = 'Age', y = 'Prevalence')

  p8 <- ggplot(data = filter(pivot.merged, Feature == 'iadl'), aes(x = Age, y = Value, color = Scenario)) +
        geom_smooth(lwd = 0.5) +
        labs(title = 'IADLs', x = 'Age', y = 'Prevalence')

@@

visCDComparisonCohort(c, s, 'No Smoke', 'cancre')
visCDComparisonCohort(c, s, 'No Smoke', 'diabe')
visCDComparisonCohort(c, s, 'No Smoke', 'hearte')
visCDComparisonCohort(c, s, 'No Smoke', 'lunge')
visCDComparisonCohort(c, s, 'No Smoke', 'stroke')
visCDComparisonCohort(c, s, 'No Smoke', 'smoken')
visCDComparisonCohort(c, s, 'No Smoke', 'employed')
visCDComparisonCohort(c, s, 'No Smoke', 'retired')
visCDComparisonCohort(c, s, 'No Smoke', 'anyadl')
visCDComparisonCohort(c, s, 'No Smoke', 'anyiadl')

@@

visList <- visCDComparisonBMI(c, bmi1, bmi2, bmi3, cds, save=TRUE)

@@

```{r}
visCDComparison(c, bmi1, 'No Obesity', 'cancre')
visCDComparison(c, bmi1, 'No Obesity', 'diabe', save=TRUE)
visCDComparison(c, bmi1, 'No Obesity', 'stroke')
visCDComparison(c, bmi1, 'No Obesity', 'hearte')
visCDComparison(c, bmi1, 'No Obesity', 'lunge')
visCDComparison(c, bmi1, 'No Obesity', 'employed')
visCDComparison(c, bmi1, 'No Obesity', 'retired')
visCDComparison(c, bmi1, 'No Obesity', 'anyadl')
visCDComparison(c, bmi1, 'No Obesity', 'anyiadl')
```
